### 2015-10-15 manuscript.Rnw
added citations for R packages listed in intro

The Open Tree of Life project provides a web interface to explore, query and
download parts of the synthetic Open Tree
(\url{http://tree.opentreeoflife.org}). Additionally, the project provides
Application Programming Interfaces (APIs) to the different services to work
programmatically with the underlying data. Here, we present \texttt{rotl} an R
package to interact with OTL's APIs using R syntax to search for, and import
phylogenetic trees and taxonomic information into R. Having access to this data
directly in R allows researchers to take advantage of the multiple packages that
are available to visualize, analyze and manipulate phylogenetic and comparative
data (e.g., ape, phytools, geiger, ggtree, phylobase, RNeXML, see
\url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list). Furthermore, \texttt{rotl} joins a growing list of R
packages that aim at accessing data from the web.

>>>>

The Open Tree of Life project provides a web interface to explore, query and
download parts of the synthetic Open Tree
(\url{http://tree.opentreeoflife.org}). Additionally, the project provides
Application Programming Interfaces (APIs) to access programmatically the
different services and underlying data. Here, we present \texttt{rotl} a package
to interact with OTL's APIs to search for and import phylogenetic trees and
taxonomic information directly in R. Having access to this data in R allows
researchers to take advantage of the multiple packages that are available to
visualize, analyze and manipulate phylogenetic and comparative data (e.g., ape
\citealt{Paradis2004}, phytools \citealt{Revell2012}, geiger
\citealt{Pennell2014-geiger}, ggtree \citealt{Yu-ggtree}, phylobase
\citealt{phylobase-0.8.0}, RNeXML \citealt{Boettiger2015}, see
\url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list). Furthermore, \texttt{rotl} joins a growing list of packages
that aim at querying and accessing data from the web directly in R for analysis.
